---
title: "Competencia"
author: "Mateo, Miguel, Steward y Camilo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# General methodology

The idea is to use Bayesian model selection using the bic approximation and a lasso regresion to select te important variables, we will try this on 100 different partitions of the data.

After that we will select only the variables that were included on at least the 50% of the partitions. We alse make sure that the distribution of the estmated $\beta$ give us a good estimation interval.

When we select the variables we estimate a glm with those variables again on 100 different partitions so that we can have an estimation of the global and the specific metric.


# Binaria

## Using Lasso



```{r bin, echo=FALSE, message=FALSE, warning=FALSE}
### Binaria

library(tidyverse)
library(BMA)
library(pROC)


train=read.csv('../data/raw/databinarystudents.csv')%>%
  dplyr::select(-id)%>%
  rename(y=yL)%>%
  filter(!is.na(y))

y=train%>%
  dplyr::select(y)%>%
  as.matrix()
x=train%>%
  dplyr::select(-y)%>%
  as.matrix()

source('funciones.R')

t=Sys.time()
semillas=as.list(1:100)

las=readRDS("las_lasso_bin.rds")

spip=prob_inc(las)
betas=get_betas(las)
colnames(betas)=colnames(x)

ok=colnames(x)[spip>0.5]
plotly::ggplotly(data.frame(betas)%>%
  dplyr::select(ok)%>%
  mutate(seed=1:nrow(betas))%>%
  gather(beta,coef,-seed)%>%
  filter(coef!=0)%>%
  ggplot(aes(x=coef,fill=beta))+geom_histogram()+facet_wrap(~beta,scales = 'free'))

x_red=data.frame(x)%>% ##quitamos x1 por el cambio de signo??
  dplyr::select(x1,x17,x18,x20,x23,x24,x4)%>%
  as.matrix()

evals=lapply(semillas,eval,x_red,y)


train=data.frame(x_red)%>%
  mutate(y=y)

model=glm(y~.,family=binomial(),data = train)
summary(model)

mets=get_met(evals)

plotly::ggplotly(data.frame(spec=mets$spec,global=mets$global)%>%
  mutate(seed=1:length(mets$spec))%>%
  gather(metrica,value,-seed)%>%
  ggplot(aes(x=metrica,y=value,fill=metrica))+
  geom_boxplot()+
  facet_wrap(~metrica,scales = 'free'))
  

#print(Sys.time()-t)

```

## BMA



```{r binbic, echo=FALSE, message=FALSE, warning=FALSE}
### Binaria

library(tidyverse)
library(BMA)
library(pROC)


train=read.csv('../data/raw/databinarystudents.csv')%>%
  dplyr::select(-id)%>%
  rename(y=yL)%>%
  filter(!is.na(y))

y=train%>%
  dplyr::select(y)%>%
  as.matrix()
x=train%>%
  dplyr::select(-y)%>%
  as.matrix()

source('funciones.R')

t=Sys.time()
semillas=as.list(1:100)

las=readRDS("las_bic_bin.rds")

spip=prob_inc(las)
betas=get_betas(las)
colnames(betas)=colnames(x)

ok=colnames(x)[spip>0.5]
plotly::ggplotly(data.frame(betas)%>%
  dplyr::select(ok)%>%
  mutate(seed=1:nrow(betas))%>%
  gather(beta,coef,-seed)%>%
  filter(coef!=0)%>%
  ggplot(aes(x=coef,fill=beta))+geom_histogram()+facet_wrap(~beta,scales = 'free'))

x_red=data.frame(x)%>% ##quitamos x1 por el cambio de signo??
  dplyr::select(x17,x23)%>%
  as.matrix()

evals=lapply(semillas,eval,x_red,y)


train=data.frame(x_red)%>%
  mutate(y=y)

model=glm(y~.,family=binomial(),data = train)
summary(model)

mets=get_met(evals)

plotly::ggplotly(data.frame(spec=mets$spec,global=mets$global)%>%
  mutate(seed=1:length(mets$spec))%>%
  gather(metrica,value,-seed)%>%
  ggplot(aes(x=metrica,y=value,fill=metrica))+
  geom_boxplot()+
  facet_wrap(~metrica,scales = 'free'))
  

#print(Sys.time()-t)

```

# Conteo

## Using Lasso



```{r con, echo=FALSE, message=FALSE, warning=FALSE}


train=read.csv('../data/raw/datacountstudents.csv')%>%
  dplyr::select(-id)%>%
  rename(y=yC)%>%
  filter(!is.na(y))

y=train%>%
  dplyr::select(y)%>%
  as.matrix()
x=train%>%
  dplyr::select(-y)%>%
  as.matrix()

source('funciones.R')

t=Sys.time()
semillas=as.list(1:100)

las=readRDS("las_lasso_con.rds")


spip=prob_inc(las)
betas=get_betas(las)
colnames(betas)=colnames(x)

ok=colnames(x)[spip>0.5]
plotly::ggplotly(data.frame(betas)%>%
  dplyr::select(ok)%>%
  mutate(seed=1:nrow(betas))%>%
  gather(beta,coef,-seed)%>%
  filter(coef!=0)%>%
  ggplot(aes(x=coef,fill=beta))+geom_histogram()+facet_wrap(~beta,scales = 'free'))

x_red=data.frame(x)%>% ##quitamos x1 por el cambio de signo??
  dplyr::select(x14,x22,x24,x25,x26,x3,x32,x4)%>%
  as.matrix()

evals=lapply(semillas,eval_c,x_red,y) ##esta con round y dio mejor


train=data.frame(x_red)%>%
  mutate(y=y)

model=glm(y~.,family="poisson",data = train)
summary(model)

mets=get_met(evals)

plotly::ggplotly(data.frame(spec=mets$spec,global=mets$global)%>%
  mutate(seed=1:length(mets$spec))%>%
  gather(metrica,value,-seed)%>%
  filter(value<10)%>%
  ggplot(aes(x=metrica,y=value,fill=metrica))+
  geom_boxplot()+
  facet_wrap(~metrica,scales = 'free'))


```

## BMA


```{r conbic, echo=FALSE, message=FALSE, warning=FALSE}
### Binaria
las=readRDS("las_bic_con.rds")



spip=prob_inc(las)
betas=get_betas(las)
colnames(betas)=colnames(x)

ok=colnames(x)[spip>0.5]
plotly::ggplotly(data.frame(betas)%>%
  dplyr::select(ok)%>%
  mutate(seed=1:nrow(betas))%>%
  gather(beta,coef,-seed)%>%
  filter(coef!=0)%>%
  ggplot(aes(x=coef,fill=beta))+geom_histogram()+facet_wrap(~beta,scales = 'free'))

x_red=data.frame(x)%>% ##quitamos x1 por el cambio de signo??
  dplyr::select(x22,x24,x25,x3)%>%
  as.matrix()

evals=lapply(semillas,eval_c,x_red,y)


train=data.frame(x_red)%>%
  mutate(y=y)

model=glm(y~.,family="poisson",data = train)
summary(model)

mets=get_met(evals)

plotly::ggplotly(data.frame(spec=mets$spec,global=mets$global)%>%
  mutate(seed=1:length(mets$spec))%>%
  gather(metrica,value,-seed)%>%
  filter(value<10)%>%
  ggplot(aes(x=metrica,y=value,fill=metrica))+
  geom_boxplot()+
  facet_wrap(~metrica,scales = 'free'))

```


# Continua 

## Lasso

```{r norlas, echo=FALSE, message=FALSE, warning=FALSE}

source('funciones.R')

train=read.csv('../data/raw/datacontinuousstudents.csv')%>%
  dplyr::select(-id)%>%
  rename(y=y)%>%
  filter(!is.na(y))

y=train%>%
  dplyr::select(y)%>%
  as.matrix()
x=train%>%
  dplyr::select(-y)%>%
  as.matrix()

las=readRDS("las_lasso_nor.rds")

spip=prob_inc(las)
betas=get_betas(las)
colnames(betas)=colnames(x)

ok=colnames(x)[spip>0.5]
plotly::ggplotly(data.frame(betas)%>%
  dplyr::select(ok)%>%
  mutate(seed=1:nrow(betas))%>%
  gather(beta,coef,-seed)%>%
  filter(coef!=0)%>%
  ggplot(aes(x=coef,fill=beta))+geom_histogram()+facet_wrap(~beta,scales = 'free'))

x_red=data.frame(x)%>% ##quitamos x1 por el cambio de signo??
  dplyr::select(x1,x6,x10,x13,x20,x23,x24,x25,x31)%>%
  as.matrix()

evals=lapply(semillas,eval_n,x_red,y) ##esta con round y dio mejor


train=data.frame(x_red)%>%
  mutate(y=y)

model=glm(y~.,family=gaussian(),data = train)
summary(model)

mets=get_met(evals)

plotly::ggplotly(data.frame(spec=mets$spec,global=mets$global)%>%
  mutate(seed=1:length(mets$spec))%>%
  gather(metrica,value,-seed)%>%
  filter(value<10)%>%
  ggplot(aes(x=metrica,y=value,fill=metrica))+
  geom_boxplot()+
  facet_wrap(~metrica,scales = 'free'))
```


## BMA

```{r norbic, echo=FALSE, message=FALSE, warning=FALSE}
### Binaria
las=readRDS("las_bic_nor.rds")


spip=prob_inc(las)
betas=get_betas(las)
colnames(betas)=colnames(x)

ok=colnames(x)[spip>0.5]
data.frame(betas)%>%
  dplyr::select(ok)%>%
  mutate(seed=1:nrow(betas))%>%
  gather(beta,coef,-seed)%>%
  filter(coef!=0)%>%
  ggplot(aes(x=coef,fill=beta))+geom_histogram()+facet_wrap(~beta,scales = 'free')

x_red=data.frame(x)%>% ##quitamos x1 por el cambio de signo??
  dplyr::select(x13,x23,x25)%>%
  as.matrix()

evals=lapply(semillas,eval_n,x_red,y)


train=data.frame(x_red)%>%
  mutate(y=y)

model=glm(y~.,family=gaussian(),data = train)
summary(model)

mets=get_met(evals)

 plotly::ggplotly(data.frame(spec=mets$spec,global=mets$global)%>%
  mutate(seed=1:length(mets$spec))%>%
  gather(metrica,value,-seed)%>%
  filter(value<10)%>%
  ggplot(aes(x=metrica,y=value,fill=metrica))+
  geom_boxplot()+
  facet_wrap(~metrica,scales = 'free'))



```
